Generating Datasets about Building Designs \\Based on a Multilayer Building Ontology

### 2015-05-01 article-00-headers.tex
Updates from ShareLaTeX
Created new figure
First version submitted
Changed bibliography style to 'splncs'
Version 1.2

\usepackage{makeidx}    % allows indexgeneration
\usepackage{graphicx}   % allows \includegraphics
\usepackage{cite}       % enables autonumbering in cites

@@

\spnewtheorem{principle}{Principle}{\bfseries}{\rmfamily}

@@

@@

\graphicspath{{images/}}

@@

% ifcOWL layer names
\newcommand{\simple}{\textbf{Simple}}
\newcommand{\standard}{\textbf{Standard}}
\newcommand{\extended}{\textbf{Extended}}

\newcommand{\ifcowl}{\textbf{ifcOWL}}
\newcommand{\ifcsimple}{\ifcowl{}-\simple{}}
\newcommand{\ifcstandard}{\ifcowl{}-\standard{}}
\newcommand{\ifcextended}{\ifcowl{}-\extended{}}
\newcommand{\ifcrdf}{\textbf{ifcRDF}}

@@

%\vspace{1cm}
%
\title{Generating Datasets about Building Designs \\Based on a Multilayer Building Ontology}
%
\titlerunning{Building ontology}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Nam Vu Hoang \and Seppo T\"orm\"a}
%
%\authorrunning{} % abbreviated author list (for running head)
%
\institute{Department of Computer Science, \\
Aalto University School of Science, 
Espoo, Finland\\
\email{\{nam.vuhoang,seppo.torma\}@aalto.fi}}

@@

The volume of data produced in the construction industry is rapidly growing but, as of now, it is not available for open and flexible access and utilization. We present an ontology derived from the conceptualization of IFC, the existing standard for representing building designs, and a tool to convert building designs from IFC files to RDF datasets that conform to the ontology. Replacing the traditional point-to-point exchange of IFC files with publication of RDF datasets using Linked Data principles and tools enables information integration across different IFC-based and other smart city datasets, and the granular access to individual components. It paves the way to a distributed and loosely coupled architecture for building information management, and provides opportunities for innovative applications.

@@

\input{article-03-bibliography.tex}

>>>>

\usepackage{makeidx}    % allows indexgeneration
\usepackage{graphicx}   % allows \includegraphics

\usepackage{cite}       % enables autonumbering in cites

@@

%\spnewtheorem{principle}{Principle}{\bfseries}{\rmfamily}

% \AtBeginDocument{
%     \newtheoremstyle{principleStyle}
%         {1.5\topsep} % Space above, default \topsep
%         {0.5\topsep} % Space below, default \topsep
%         {\itshape} % Body font
%         {} % Indent amount, example: \parindent
%         {\bfseries\itshape} % Theorem head font
%         {.} % Punctuation after theorem head
%         {.5em} % Space after theorem head
%         {} % Theorem head spec (can be left empty, meaning `normal')

%     \theoremstyle{principleStyle} \newtheorem{principle}{Principle}
% }

\usepackage{titlesec}   % enables \titlespacing

\titlespacing*{\section}
    {0pt}{\baselineskip}{0.5\baselineskip}    % {<left>}{<before-sep>}{<after-sep>}

\titlespacing*{\subsection}
    {0pt}{0.8\baselineskip}{0.5\baselineskip}

\titlespacing*{\subsubsection}
    {0pt}{0.8\baselineskip}{0.5em}

@@

%
% THEOREMS
%
%\usepackage{amsthm} % enables \newtheorem{}{}

@@

% \graphicspath{{images/}}

\usepackage{caption}    % enables \captionsetup for tables and figures

\AtBeginDocument{
    \captionsetup{font=small}
    \captionsetup{labelfont=bf}
    % \captionsetup[table]{aboveskip=0pt}
    \captionsetup[table]{belowskip=0pt}

    % \setlength{\textfloatsep}{10pt}  % distance between floats on the top or the bottom and the text;
    % \setlength{\floatsep}{0pt}      % distance between two floats;
    \setlength{\intextsep}{\baselineskip}     % distance between floats inserted inside the page text (using h) and the text proper.

%     The default values in the article document class with the 10pt option are:
% \textfloatsep: 20.0pt plus 2.0pt minus 4.0pt;
% \floatsep: 12.0pt plus 2.0pt minus 2.0pt;
% \intextsep: 12.0pt plus 2.0pt minus 2.0pt.
}

%
% REFERENCES
%

% \usepackage[sorting=none]{biblatex} % http://www.ctan.org/tex-archive/help/Catalogue/entries/biblatex.html

@@

% ifcOWL layer names
\newcommand{\bname}[1]{\textnormal{\textbf{#1}}}

\newcommand{\simple}{\bname{Simple}}
\newcommand{\standard}{\bname{Standard}}
\newcommand{\extended}{\bname{Extended}}

\newcommand{\ifcowl}{\bname{ifc\-OWL}}
\newcommand{\ifcrdf}{\bname{ifc\-RDF}}
\newcommand{\ifcsimple}{\ifcowl{}-\simple{}}
\newcommand{\ifcstandard}{\ifcowl{}-\standard{}}
\newcommand{\ifcextended}{\ifcowl{}-\extended{}}

\newcommand{\ifcconverter}{\bname{IFC2LD}}
\newcommand{\ifcld}{\ifcconverter}

@@

%\vspace{1cm}
%
\title{Generating Datasets about Building Designs \\Based on a Multilayer Building Ontology}
%
% \titlerunning{Building ontology}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Nam Vu Hoang \and Seppo T\"orm\"a}
%
%\authorrunning{} % abbreviated author list (for running head)
%
\institute{Department of Computer Science, \\
Aalto University School of Science, 
Espoo, Finland\\
\email{\{nam.vuhoang,seppo.torma\}@aalto.fi}}

@@

The volume of data produced in the construction industry is rapidly growing but, as of now, it is not available for open, flexible access and utilization. We propose a new approach to the automatic derivation of a building ontology from the conceptualization of Industry Foundation Classes (IFC), the existing standard for representing building designs. The resulted multilayer ontology and the tool for converting building designs from IFC files to RDF datasets that conform to the ontology are introduced. Replacing the traditional point-to-point exchange of IFC files with publication of RDF datasets using Linked Data tools enables information integration across different IFC-based and other smart city datasets, and the granular access to individual components. It paves the way to a distributed, loosely coupled architecture for building information management, and provides opportunities for innovative applications.

@@

% According to LNCS manual, the Acknowledgements section must be declared by using \subsubsection{}

\subsubsection{Acknowledgements.} This work has been carried out at Aalto University in research projects DRUM (RYM/PRE 2010-2014) and DRUMBEAT (2014-2017), funded by Tekes, Aalto University, and the participating companies.

%\input{article-03-bibliography.tex}

% \bibliographystyle{splncs03}
\bibliographystyle{splncs}
\bibliography{article.bib}

% \printbibliography{}

### 2015-05-01 article-01-introduction.tex
Version 1.2

Currently, huge amounts of information about building designs is produced  
using Building Information Modeling (BIM) tools \cite{eastman2011bim}. A widely adopted standard, 
IFC (Industry Foundation Classes) \cite{ISO16739,liebich2010unveiling} provides a common representation for BIM models of 
different design disciplines. All major BIM tools support IFC and can export BIM models to IFC files for exchange with other parties.

BIM models could provide a natural framework to organize and manage building related information. However, a big obstacle is the difficulty to access and utilize BIM models which have traditionally been shared through point-to-point file exchange. They cannot be used in an online, granular, and 
interlinked manner. This provides a poor basis for open utilization of building information and the 
emergence of new, innovative applications.
To make BIM models accessible on the Web \cite{torma2014wobd}, we have developed the 
\bname{IFC2LD converter} to 
derive OWL ontologies from the IFC schema (\ifcowl{}), and RDF datasets from IFC files 
(\ifcrdf{}). The \ifcowl{} specifies concepts, relations, and constraints for \ifcrdf{} datasets that replicate the content of IFC files. 
All terms defined in \ifcowl{}  must thus be based on the corresponding constructs in 
the IFC schema.

@@

The conversion of IFC files to \ifcrdf{} is straightforward and can be done 
without information loss.
Ideally, there would also be just one \ifcowl{} ontology for each version of the IFC schema. However,
there are possibilities and reasons to convert the IFC schema to OWL in several different ways. Firstly, there is a \emph{mismatch} between the modeling constructs of OWL and 
EXPRESS data definition language \cite{schenck1994information} used to specify the IFC schema. Secondly, a simple version of \ifcowl{} \emph{compatible with
restricted OWL profiles} (OWL 2 EL or QL) \cite{motik2012owl} is useful to support ontology
reasoning or inexact reasoning. Thirdly, for most practical purposes only a subset of ontology
information is required, as no validation or checking of \ifcrdf{} data is needed; it can
be considered \emph{practically valid} w.r.t. the schema, since BIM tools use certified converters. Moreover, icfRDF can sensibly only be used in a
\emph{read-only} fashion, since BIM models will be maintained in the native formats of BIM
tools. In addition, a full conversion of the IFC schema produces a huge ontology, difficult to understand or manipulate.

Consequently, we convert the IFC schema into a \emph{flexible, multilayer \ifcowl{} ontology}
in a way that \emph{\ifcrdf{} is compatible with any of the layers} (Fig. \ref{fig:ifcOWL-layers}). 
New representational constructs are introduced at more comprehensive levels which therefore 
provide increasing detailed type information about \ifcrdf{} data:

\vspace{0.5\topsep}
\noindent
\begin{scriptsize}
\begin{center}
    \def\arraystretch{1.2}
    \setlength{\tabcolsep}{6pt}
    \begin{tabularx}{0.95\textwidth}{|l|l|X|}
        \hline
            \textbf{Layer} & \textbf{Profile} & \textbf{Included schema information} \\
        \hline
            ifcOWL-Simple & OWL 2 EL or & Schema meta data plus: \\
            & OWL 2 QL or & \ \ - All type definitions and hierarchies \\
            & OWL 2 RL & \ \ - All entity type properties (names, range types) \\
        \hline 
            ifcOWL-Standard & OWL 2 RL & All above plus: \\
            & & \ \ - All entity type keys \\
            & & \ \ - All entity type inverse properties \\
        \hline
            ifcOWL-Extended & OWL 2 RL & All above plus: \\
            & & \ \ - All cardinality constraints \\
        \hline
    \end{tabularx}
\end{center}
\end{scriptsize}

@@

From the previous IFC-to-OWL/RDF conversions
\cite{beetz2005ontology,beetz2009ifcowl,pauwels2011interoperability} our approach differs since it
is based on OWL 2 profiles, produces a flexible multilayer ontology, applies other methods of data\-type definitions and is specifically targeted to
real-life Linked Data applications. It uses stable URIs for entities, in contrast to the previous approaches
where the URIs were instable across models versions.

CityGML \cite{kolbe2005citygml} is a surface model for buildings, which can be useful to visitors for 
indoor navigation. IFC contains complementary information about building design, structure, 
and equipment for a wider range of stakeholders and use cases. Moreover, IFC data can be one source 
when generating CityGML models. % GityGML has also been converted into OWL.

In the rest of this paper we describe the conversions to \ifcowl{} and \ifcrdf{}, present the deployment of ontologies, example datasets and the converter, and finish with summary and future work.

>>>>

Currently, huge amounts of building designs information is produced by 
using Building Information Modeling (BIM) tools \cite{eastman2011bim}. 
IFC \cite{ISO16739,liebich2010unveiling} -- a widely adopted standard -- provides a common representation for BIM models of 
different design disciplines. All major BIM tools support IFC and can export BIM models to IFC files for exchange with other parties.

BIM models could provide a natural framework to organize and manage building related information. However, a big obstacle is the difficulty to access and utilize BIM models which have traditionally been shared through point-to-point file exchange. They cannot be used in an online, granular, and 
interlinked manner. This provides a poor basis for open utilization of building information and the 
emergence of new, innovative applications.
To make BIM models accessible on the Web \cite{torma2014wobd}, we have developed the 
\bname{IFC2LD converter} to 
derive OWL ontologies from the IFC schema (\ifcowl{}), and RDF datasets from IFC files 
(\ifcrdf{}). The \ifcowl{} specifies concepts, relations, and constraints for \ifcrdf{} datasets that replicate the content of IFC files. 
Thus, all terms defined in \ifcowl{}  must be based on the corresponding constructs in 
the IFC schema.

@@

The conversion of IFC files to \ifcrdf{} is straightforward and can be done 
without information loss.
Ideally, there would be just one \ifcowl{} ontology for each version of the IFC schema. However,
there are possibilities and reasons to convert the IFC schema to OWL in several different ways. Firstly, there is a \emph{mismatch} between the modeling constructs of OWL and the 
EXPRESS data definition language \cite{schenck1994information} used to specify the IFC schema. Secondly, a simple version of \ifcowl{} that is \emph{compatible with
restricted OWL profiles} (OWL 2 EL or QL) \cite{motik2012owl} is useful to support ontology
reasoning or inexact reasoning. Thirdly, for most practical purposes only a subset of ontology
information is required, as no validation or checking of \ifcrdf{} data is needed; it is considered \emph{practically valid} w.r.t. the schema, since BIM tools use certified converters. Moreover, \ifcrdf{} can sensibly only be used in a
\emph{read-only} fashion, since BIM models will be maintained in the native formats of BIM
tools. In addition, a full conversion of the IFC schema produces a huge ontology, difficult to understand or manipulate.

Consequently, we convert the IFC schema into a \emph{flexible, multilayer \ifcowl{} ontology}
in a way that \emph{\ifcrdf{} is compatible with any of the layers} (Fig. \ref{fig:ifcOWL-layers}). 
New representational constructs are introduced at more comprehensive levels which, therefore, 
provide increasing detailed type information about \ifcrdf{} data (Table \ref{tab:ifcOWL-layers}).

\begin{table}
    \caption{Contents of ifcOWL layers}
    \label{tab:ifcOWL-layers}
    \centering
    \scriptsize
    \def\arraystretch{1.2}          % vertical space
    \setlength{\tabcolsep}{6pt}     % horizontal space
    \begin{tabularx}{0.95\textwidth}{|l|l|X|}
        \hline
            \textbf{Layer} & \textbf{Compatible profile} & \textbf{Contents} \\
        \hline
            ifcOWL-Simple & OWL 2 EL or & Ontology meta data plus: \\
            & OWL 2 QL or & \ \ - All basic constructs \\
            & OWL 2 RL & \ \ - All type definitions and hierarchies \\
        \hline 
            ifcOWL-Standard & OWL 2 RL & All above plus: \\
            & & \ \ - All entity type properties and keys \\
        \hline
            ifcOWL-Extended & OWL 2 RL & All above plus: \\
            & & \ \ - All cardinality constraints \\
        \hline
    \end{tabularx}
\end{table}

@@

Our approach differs from the previous IFC-to-OWL/RDF conversions
\cite{beetz2005ontology,beetz2009ifcowl,pauwels2011interoperability}. It
is based on OWL 2 profiles, produces a flexible multilayer ontology, applies other methods of data\-type definitions and is specifically targeted to
real-life Linked Data applications. It uses stable URIs for entities, in contrast to the previous approaches
where the URIs were unstable across models versions.

CityGML \cite{kolbe2005citygml}, a surface model for buildings, can be useful to visitors for 
indoor navigation. IFC contains complementary information about building design, structure, 
and equipment for a wider range of stakeholders and use cases. Moreover, IFC data can be one source 
when generating CityGML models. % GityGML has also been converted into OWL.

\TODO{Update the description of sections}

In the rest of this paper, we describe the conversions to \ifcowl{} and \ifcrdf{}, present the deployment of ontologies, example datasets and the converter, and finish with summary and future work.
